workshop

### 2023-03-14 scripts/workshop/workshop.Rmd
more host stuff

@@

supp1_raw
supp1_log10
```

@@

>>>>

vl %<>% mutate(ln_of_mean = log(mean))

@@

supp1_ln <- vl %>% arrange(ln_of_mean) %>% 
  mutate(abb_name = factor(abb_name, levels = abb_name)) %>% 
  ggplot(.,aes(x=abb_name,y=ln_of_mean)) +
  geom_point() + 
  xlab("Species") + ylab("ln(Viral Load)") + 
  geom_hline(yintercept = 1) + 
  labs(title = "Viral Loads") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  scale_y_continuous(breaks=seq(0,6,1))

supp1_raw
supp1_log10
supp1_ln
```

@@

First and last sighting of each at each wetland
```{r}
ph_range <- ph_pa %>% filter(value==1) %>% group_by(name, WetAltID) %>% summarize(min_mo=min(Month.1), max_mo = max(Month.1))
ph_range %<>% mutate(first = as.numeric(gsub("Month","",min_mo)),
                     last = as.numeric(gsub("Month","",max_mo)))
ph_range_summ <- ph_range %>% group_by(name) %>% summarize(mean_first = mean(first),
                                                           mean_last = mean(last))

ph_range_summ %<>% mutate(Species = as.numeric(gsub("PA","",name)))

ph_range_summ %<>% left_join(.,vl)

ph_range_summ %>% arrange(mean) %>% mutate(name=factor(name, levels=name)) %>% filter(!is.na(species_name)) %>% 
  ggplot(.,aes(y = name, color=ln_of_mean)) +
  geom_linerange(aes(xmin=mean_first,xmax=mean_last,linewidth=1)) + 
  scale_color_viridis_c()
```

Do this instead with abundance
```{r}
ph_ab_summ <- ph_ab %>% mutate(log1p_value = log1p(value)) %>% group_by(name,Month.1) %>% summarize(log1p_ab_mean = mean(log1p_value),
                                                                                                    ab_mean = mean(value)) %>% ungroup()

ph_ab_summ %<>% mutate(Species = as.numeric(gsub("AB","",name)))

ph_ab_summ %<>% left_join(.,vl)

ph_ab_summ %>% arrange(mean) %>% mutate(name=factor(name, levels=unique(name))) %>% filter(!is.na(species_name)) %>% 
              ggplot(., aes(x=Month.1,
                            y=name,
                            group=name,
                            fill=as.factor(mean),
                            height = ab_mean)) +
  geom_density_ridges_gradient(show.legend = T, stat = "identity") + labs(x = "Absolute Abundance")

ph_ab_summ %>% arrange(mean) %>% mutate(name=factor(name, levels=unique(name))) %>% filter(!is.na(species_name)) %>% 
              ggplot(., aes(x=Month.1,
                            y=name,
                            group=name,
                            fill=as.factor(mean),
                            height = log1p_ab_mean)) +
  geom_density_ridges_gradient(show.legend = T, stat = "identity") + labs(x = "log1p(Abundance)")

ph_ab_summ %>% arrange(desc(mean)) %>% mutate(name=factor(name, levels=unique(name))) %>% filter(!is.na(species_name)) %>% 
              ggplot(., aes(x=Month.1,
                            y=log1p_ab_mean,
                            fill=as.factor(ln_of_mean))) +
  geom_col() + labs(x = "log1p(Abundance)") + facet_wrap(vars(name), ncol=1) + theme(strip.background = element_blank(),
                                                                                     strip.text.x = element_blank())
```
